\documentclass[12pt,letterpaper]{hmcpset}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}

% info for header block in upper right hand corner

\newcommand{\pn}[1]{\left( #1 \right)}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\bk}[1]{\left[ #1 \right]}

\newcommand{\vb}{\mathbf{v}}
\newcommand{\ub}{\mathbf{u}}
\newcommand{\fx}{f \left( x \right) =}
\newcommand*\LH{\ensuremath{\overset{\kern2pt L'H}{=}}}
\renewcommand{\labelenumi}{{(\alph{enumi})}}

\newcommand{\Zz}{\mathbb{Z}}
\newcommand{\Rr}{\mathbb{R}}
\newcommand{\Qq}{\mathbb{Q}}
\newcommand{\Cc}{\mathbb{C}}

\begin{document}

\begin{problem}
You've made it to the \$1 million question, but it's a tough one. 
Out of the four choices, A, B, C and D, you're 70 percent sure the answer is B, 
and none of the remaining choices looks more plausible than another. 
You decide to use your final lifeline, the 50:50, which leaves you with two possible answers, one of them correct.
Lo and behold, B remains an option! How confident are you now that B is the correct answer?	
\end{problem}

\begin{solution}
Since there is no difference relevant to this problem between A, C, and D, let us for convenience assume that after we
invoke our 50:50, the possible answers remaining are A and B. The 50:50 has given us the information that either A or
B is the right answer. We then want to find the probability that, given that A or B is correct, B is correct. We can
invoke Bayes' Theorem to see that that probability is equal to
$$P(B | A \cup B) = \frac{P(A \cup B | B)P(B)}{P(A \cup B)}.$$
The probability that either A or B is correct given that B is correct is clearly 1, so the $P(A \cup B | B)$ disappears
from our equation, leaving us with
$$P(B | A \cup B) = \frac{P(B)}{P(A \cup B)}.$$
This we can determine from the probabilities we knew before invoking the 50:50. $P(B) = .7$, and the remaining $.3$ of
probability was divided evenly between A, C, and D, so $P(A) = .1$. Thus $P(A \cup B) = .8$, and therefore
$$P(B | A \cup B) = \frac{.7}{.8} = .875.$$
Hence, you can now be 87.5 percent confident that B is the correct answer.
\vfill
\end{solution}
\newpage

\end{document}
